Prediction of PIK3CA mutations from cancer gene expression data

### 2020-06-11 plosOne/plosOne.tex
PRS

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Prediction of PIK3CA mutation with gene expression in cancer} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jun Kang\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}},
Ahwon Lee\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}},
Youn Soo Lee\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}}\textsuperscript{*}\\
\bigskip
\textbf{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}}Department of Hospital Pathology, Seoul St.~Mary's Hospital, College of
Medicine, The Catholic University of Korea, Seoul, South Korea\\
\bigskip
* Corresponding author: lys9908@catholic.ac.kr\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Breast cancer with PIK3CA mutation has been approved to use PIK3CA
inhibitor in hormone receptor-positive HER2 negative subtype. We apply a
supervised elastic net penalized logistic regression model in prediction
PIK3CA mutation from gene expression data. Penalized logistic regression
was applied to prediction modeling using the TCGA pan-cancer dataset.
10845 cases were available for both PIK3CA mutation and mRNA expression
data. In 10-fold cross-validation, the model with \(\lambda\) = 0.01 and
\(\alpha\) = 1.0 (Ridge regression) showed best performance in terms of
AUROC. The final model was trained with the selected hyperparameters
with the entire trainset. The trainset AUROC was 0.93 and the testset
AUROC was 0.84. The AUPR of trainset was 0.66 and the testset AUPR was
0.39. The cancer types were the most important predictors. Both IGFR1R
and PTEN were most important among gene expression predictors. Our study
suggests that the prediction of genomic alteration with gene expression
data is possible with good performance.

@@

Targeted therapy becomes a standard treatment in many cancer patients.
The majority of targeted therapy requires a test for a specific cancer
genomic alteration, to treat the patients. Many direct tests for the
genomic alteration have been developed and prooved for their clinical
utility to find which patients will be responding to the targeted
therapy.

It has been actively researched that the machine learnig approach can be
applied to detect genomic alterations. Machine learning algorithm can
build a prediction model from a large number of predictors such as
radiolomic features {[}1{]}, pathology image {[}2{]} or gene expression
data {[}3{]}. Because the most direct genomic test is more specific and
sensitive than predictive models, the machine learning approach might
have a limited role in clinical practice. However, the machine learning
prediction can be a second-best when the direct test fails.

Prediction of RAS pathway activation with gene expression data was done
in the previous study. {[}5{]} They trained pan-cancer The Cancer Genome
Atlas (TCGA) data with a supervised elastic net penalized logistic
regression classifier with stochastic gradient descent. The performance
of their model was 84\% with an area under the receiver operating
characteristic (AUROC) curve and 63\% with an area under the
precision-recall (AUPR) curve. The authors suggested their approach can
be applied to other genomic alterations.

Breast cancer with PIK3CA mutation has been approved to use PIK3CA
inhibitor in hormone receptor-positive HER2 negative subtype. {[}6{]}
The PIK3CA mutation is the second most driver mutation after TP53. The
PIK3CA mutation is most frequently founded in endometrial carcinoma
(45\%), and followed by breast invasive carcinoma (24\%), cervical
squamous cell carcinoma, and endocervical adenocarcinoma (20\%) and
colon adenocarcinoma (16\%).

PIK3CA encodes the p110\(\alpha\) catalytic subunit of
phosphatidylinositol 3′-kinase (PI3K). PI3K is a protein kinase that
phosphorylates phosphatidylinositol 4,5-biphosphate
(PIP\textsubscript{2}) to make phosphatidylinositol 3,4,5-triphosphate
(PIP\textsubscript{3}). Phosphatase and tensin homolog (PTEN) changes
PIP\textsubscript{2} to PIP\textsubscript{3} in contrast, PI3K.
PIP\textsubscript{3} is a second messenger to activate protein kinase B
(AKT) which is a serine/threonine-specific protein kinase. AKT inhibits
apoptosis and promotes cell proliferation. {[}7{]}

We apply a supervised elastic net penalized logistic regression model in
prediction PIK3CA mutation. The purpose of this study is to know whether
this prediction model approach can be applied not only to RAS pathway
activation but also PIK3CA mutation across many cancer types.

@@

We used the TCGA pan-cancer dataset. TCGA is a cancer genomic consortium
that archives data of exome sequencing, gene expression, DNA
methylation, protein expression, and clinical data of more than 10000
cancer samples across 33 common cancer types. The TCGA dataset is
publically available. PIK3CA mutation data was got using cgdsr
rpackage.{[}8{]} Gene expression data was downloaded from the National
Cancer Institute (NCI)'s Genomic Data Commons (GDC) website that
archives data used for The Pan-Cancer Atlas initiative.
(https://gdc.cancer.gov/about-data/publications/pancanatlas) The gene
expression TCGA pan-cancer dataset is batch-corrected with
normalization.

The target variable was the PIK3CA mutation status. The status of PIK3CA
was considered as positive when the case has following PIK3CA variants
which are the target variants of the therascreen PIK3CA RGQ PCR Kit;
C420R, E542K, E545A, E545D, E545G, E545K, Q546E, Q546R, H1047L, H1047R,
H1047Y. The therascreen PIK3CA RGQ PCR Kit was approved as a companion
diagnostics to treat with PIK3CA inhibitor by the U.S. Food and Drug
Administration. We split the three-quarters of the dataset for the
trainset and one quarter for the test set.

@@

To narrow down potential predictors, genes with a large the median
absolute deviation (more than third-quartiles) were selected. 33 cancer
type dummy variables were included in predictor variables. Yeo-Johnson
transformation was done to correct skewness. Centering and scaling were
done. All preprocessing was done using recipe r package. {[}9{]}
Penalized logistic regression was applied to prediction modeling.
10-fold cross-validation with targe variable stratification was done
over the hyperparameter grid: \(\lambda\) \{\(10^{-5}\),
\(10^{-4}\),\(10^{-3}\),\(10^{-2}\),\(10^{-1}\), \(10^{0}\)\},
\(\alpha\) \{0.0, 0.25, 0.5, 0.75\}. Lambda is penalty scaling parameter
and alpha is mixing parameter of penalty function
(\((1-\alpha)/2 \lVert\beta\rVert_2^2+\alpha\lVert \beta \rVert_1\)).
{[}10{]}

@@

Model performance was evaluated with the AUROC curve and the AUPR curve.
The AUPR is more informative than AUROC on imbalanced datasets. {[}11{]}
The modeling process and accessing model performance were done with
tidymodels rpackage. {[}12{]}

@@

10845 cases were available for both PIK3CA mutation and mRNA expression
data. 5128 out of 20502 genes were included in the modeling process
after filtering with median absolute deviation as described at the
modeling process method. The prevalence rate of PIK3CA was 0.11 in all
cases. The PIK3CA prevalence rate of each cancer type varied. The median
prevalence rate of PIK3CA of each cancer type was 0.03 (range 0-0.33)
(Figure 1).

@@

In 10-fold cross-validation, the model with \(\lambda\) = 0.01 and
\(\alpha\) = 1.0 (Ridge regression) showed best performance in terms of
AUROC. The final model was trained with the selected hyperparameters
with the entire trainset. The trainset AUROC was 0.93 and the testset
AUROC was 0.84. The AUPR of trainset was 0.66 and the testset AUPR was
0.39. (Figure 2A)

@@

Figure 3 shows the top 30 important predictors. The coefficient is the
parameter of the predictor which represents the effect of the predictor
on prediction. IGF1R mRNA expression was the strongest negative
predictor and PTEN was the strongest positive predictor. Both IGFR1R and
PTEN are key players in the tyrosine kinase pathway. The cancer types
were important predictors. Some cancer types including uterine
carcinosarcoma (UCS), bladder urothelial carcinoma (BLCA), pancreatic
adenocarcinoma (PAAD), lymphoid neoplasm diffuse large B-cell lymphoma
(DLBC) are the strongest predictors.

@@

Our model showed good performance to predict the PIK3CA mutation of
various cancer types. This result suggests that the supervised elastic
net penalized logistic regression model can be applied not only to the
RAS activation pathway but also other genomic alterations. Both the RAS
activation pathway and PIK3CA mutation are important and common cancer
genomic alterations. They have a significant effect on gene expression
in cancer cells. It can not be generalized that the supervised elastic
net penalized logistic regression model can be applied to other genomic
alteration. It might be a challenging prediction of genomic alterations
that are infrequent or have a weak effect on gene expression.

Prediction modeling from the TCGA pan-cancer dataset has limitations
regarding data preprocessing. The gene expression data is processed
between-sample normalization to remove the batch effect. If the model
has been trained from the between-sample normalization, a new sample can
not be exactly preprocessed with normalization which was done on
trainset. A model based on gene expression TCGA pan-cancer dataset has a
limitation on data preprocessing. It is necessary for developing a
preprocessing method that is independent with a dataset to apply the
gene expression data to the prediction model.

Our PIK3CA prediction model performed similar with the RAS activation
prediction model of the previous study in terms of AUROC (0.84). However
AUPR of our model for PIK3CA is lower than model for RAS activation
(0.39 vs 0.63). The reason of lower AUPR of our model can be explained
by low prevalence rate of PIK3CA mutation and imbalanced dataset. The
model for RAS activation trained with cancer types with more than 0.05
prevalence of RAS activation to avoid imbalance classification problem.
We included all cancer types into modeling process. The lower prevalance
rate of target variable mean our dataset has a lower baseline of AUPR.
In the subanalysis for performance of each cancer types, the cancer
types with higher PIK3CA mutation rate showe better AUPR.

Our model includes cancer type as predictors and they are stronger
predictors than gene expression. The varying prevalence of PIC3CA
mutation across cancer type might reason for the strong predictive power
of cancer type. If the cancer type was wrong or can not be determined,
our model performance can be poor.

Some significant gene expression predictors were closely related to PTEN
and the PI3K pathway. PTEN and IGFR1R are the strongest gene expression
predictor which have negative and positive predictive power. IGF1R is a
tyrosine kinase receptor that activates PI3K. {[}13{]} PTEN is an
important regulator of PIP\textsubscript{3} by dephosphorylating
PIP\textsubscript{3} in contrast PI3K.{[}7{]}

There is some study trying to predict genomic alterations from gene
expression data. A study performed PIK3CA mutation prediction by a
gene-expression signature which is a sum of the average of the
logarithmic gene expression. The model showed good performance AUROC
0.71 in an independent test set. {[}4,14{]} Another study predicted copy
number alterations with gene expression using a multinomial logistic
regression model with least absolute shrinkage and selection operator
(LASSO). The prediction of the 1p/19q codel was very good with an AUROC
of 0.997. The gene-level prediction was good with an AUROC 0.75.
{[}15{]} A Hidden Markov Model Approach for Prediction of Genomic
Alterations from Gene Expression Profiling.{[}16{]} A logistic
regression model was used for MYCN gene amplification in neuroblastoma.
{[}17{]}

Our study suggests that the prediction of genomic alteration with gene
expression data is possible with good performance. However, improvement
of performance is required for applying to clinical test and the
standardization of generation processing of gene expression data is also
needed.

@@

\begin{itemize}
\item
  Figure 1. Prevalence rate of PIK3CA across cancer types. The
  abbreviations of cancer types are explained in the S1 Appendix.
\item
  Figure 2. Summary of modeling results
\end{itemize}

\begin{enumerate}
\def\labelenumi{(\Alph{enumi})}
\tightlist
\item
  Left: receiver operating characteristic (ROC) curve. right:
  precision-recall (PR) curve of trainset and test set. The horizontal
  green line is the PIK3CA mutation rate (0.11) (B) Correlation between
  trainset and test set of the area under the receiver operating
  characteristic curve (AUROC) and the area under the precision-recall
  curve (AUPR) among cancer type. The gray band is 95\% confidence
  interval. The abbreviations are explained in the S1 Appendix. (C)
  Correlation between the PIK3CA mutation rate of the AUROC and the
  AUPR.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Figure 3. Coefficients of model
\end{itemize}

\begin{enumerate}
\def\labelenumi{(\Alph{enumi})}
\tightlist
\item
  Top 30 high coefficients of mRNA. (B) Coefficients of cancer types.
  The abbreviations of cancer types are explained in the S1 Appendix.
\end{enumerate}

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Prediction of PIK3CA mutation with gene expression in cancer} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Jun Kang\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}},
Ahwon Lee\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}},
Youn Soo Lee\textsuperscript{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}}\textsuperscript{*}\\
\bigskip
\textbf{\getAff{Department of Hospital Pathology, Seoul St.~Mary's Hospital}}Department of Hospital Pathology, Seoul St.~Mary's Hospital, College of
Medicine, The Catholic University of Korea, Seoul, South Korea\\
\bigskip
* Corresponding author: lys9908@catholic.ac.kr\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Breast cancers with PIK3CA mutations can be treated with PIK3CA
inhibitors in hormone receptor-positive HER2 negative subtypes. We
applied a supervised elastic net penalized logistic regression model to
predict PIK3CA mutations from gene expression data. This regression
approach was applied to predict modeling using the TCGA pan-cancer
dataset. Approximately 10,845 cases were available for PIK3CA mutation
and mRNA expression data. In 10-fold cross-validation, the model with
\(\lambda\) = 0.01 and \(\alpha\) = 1.0 (Ridge regression) showed the
best performance, in terms of area under the receiver operating
characteristic (AUROC). The final model was developed with selected
hyper-parameters using the entire train-set. The train-set AUROC was
0.93, and the test-set AUROC was 0.84. The area under the
precision-recall (AUPR) of the train-set was 0.66, and the test-set AUPR
was 0.39. Cancer types were the most important predictors. Both IGFR1R
and the phosphatase and tensin homolog (PTEN) were the most significant
genes in gene expression predictors. Our study suggests that predicting
genomic alterations using gene expression data is possible, with good
outcomes.

@@

Targeted therapy has become a standard treatment for many cancer
patients, however the approach requires a test for a specific cancer
genomic alteration, to treat patients. Several direct genomic alteration
tests have been developed and proven for their clinical utility to treat
patients. Machine learning approaches can be applied to detect genomic
alterations . Machine learning algorithms can build prediction models
from a large number of predictors, such as radiomic features {[}1{]},
pathology image {[}2{]} or gene expression data {[}3{]}. Because most
direct genomic tests are more specific and sensitive than predictive
models, machine learning approaches may have limited roles in clinical
practice, however, machine learning approaches are ideal when direct
tests are unavailable or fail. RAS pathway activation predictions have
been performed using gene expression data {[}5{]}. Authors used data
from The Cancer Genome Atlas (TCGA), with a supervised elastic net
penalized logistic regression classifier, with stochastic gradient
descent. Their model performance was 84\% with an area under the
receiver operating characteristic (AUROC) curve, and 63\% with an area
under the precision-recall (AUPR) curve. Importantly, these authors
suggested their approach could be applied to other genomic alterations.
Breast cancer expressing PIK3CA mutations can be treated using PIK3CA
inhibitors, in hormone receptor-positive HER2 negative subtypes {[}6{]}.
The PIK3CA mutation is the second most common driver mutation after
TP53, and is most frequently detected in endometrial carcinoma (45\%),
followed by breast invasive carcinoma (24\%), cervical squamous cell
carcinoma, endo-cervical adenocarcinoma (20\%) and colon adenocarcinoma
(16\%). PIK3CA encodes the p110\(\alpha\) catalytic subunit of
phosphatidylinositol 3′-kinase (PI3K). PI3K is a protein kinase that
phosphorylates phosphatidylinositol 4,5-biphosphate
(PIP\textsubscript{2}) to generate phosphatidylinositol
3,4,5-triphosphate (PIP\textsubscript{3}). The phosphatase and tensin
homolog (PTEN) converts PIP\textsubscript{2} to PIP\textsubscript{3} in
contrast to PI3K. PIP\textsubscript{3} is a second messenger that
activates protein kinase B (AKT), which is a serine/threonine-specific
protein kinase. AKT inhibits apoptosis and promotes cell proliferation
{[}7{]}.

We applied a supervised elastic net penalized logistic regression model
to predict PIK3CA mutations. We wanted to ascertain whether this
prediction model approach could be applied not only to RAS pathway
activation, but also to PIK3CA mutation predictions across several
cancer types.

@@

We used the TCGA pan-cancer dataset. TCGA archives the following; exome
sequencing, gene expression, DNA methylation, protein expression, and
clinical data from \textgreater{} 10,000 cancer samples across 33 common
cancer types. The TCGA dataset is publically available. PIK3CA mutation
data was extracted using cgdsr rpackage {[}8{]}. Gene expression data
was downloaded from the National Cancer Institute (NCI)'s Genomic Data
Commons (GDC) website. This archives data for TCGA
(https://gdc.cancer.gov/about-data/publications/pancanatlas). Gene
expression in the TCGA pan-cancer dataset is batch-corrected with
normalization. The target variable was PIK3CA mutation status. PIK3CA
status was considered positive when the case had the following PIK3CA
variants, which were the target variants of the Therascreen PIK3CA RGQ
PCR Kit ; C420R, E542K, E545A, E545D, E545G, E545K, Q546E, Q546R,
H1047L, H1047R, H1047Y. This kit was approved as a companion diagnostics
test to treat with PIK3CA inhibitor by the United States Food and Drug
Administration. We split three-quarters of the dataset into the
train-set and one quarter into the test-set.

@@

To narrow down potential predictors, genes with a large median absolute
deviation (\textgreater{} third-quartiles) were selected. Thirty three
cancer type dummy variables were included in predictor variables.
Yeo-Johnson transformation was performed to correct skewness. Centering
and scaling were also performed. All preprocessing was performed using
the recipe r package {[}9{]}. Penalized logistic regression was applied
to prediction modeling. Ten-fold cross-validation with targe variable
stratification was performed over the hyper-parameter grid: \(\lambda\)
\{\(10^{-5}\), \(10^{-4}\),\(10^{-3}\),\(10^{-2}\),\(10^{-1}\),
\(10^{0}\)\}, \(\alpha\) \{0.0, 0.25, 0.5, 0.75\}. Lambda (\(\lambda\))
is a penalty scaling parameter and alpha (\(\alpha\)) is a mixing
parameter of penalty function
(\((1-\alpha)/2 \lVert\beta\rVert_2^2+\alpha\lVert \beta \rVert_1\))
{[}10{]}.

@@

Model performance was evaluated using AUROC and AUPR curve approaches.
The AUPR approach is more informative than AUROC for imbalanced datasets
{[}11{]}. The modeling process and accessing model performance were
performed with the tidymodels rpackage {[}12{]}.

@@

10,845 cases were available for both PIK3CA mutation and mRNA expression
data. 5,128 out of 20,502 genes were included in the modeling process,
after filtering for median absolute deviation, as described in the
modeling process method. The prevalence rate for PIK3CA was 0.11 in all
cases. The PIK3CA prevalence rate in each cancer type varied. The median
prevalence rate of PIK3CA for each cancer type was 0.03 (range 0--0.33)
(Figure 1).

@@

For 10-fold cross-validation, the model with \(\lambda\) = 0.01 and
\(\alpha\) = 1.0 (Ridge regression) showed the best performance in terms
of AUROC. The final model was trained with the selected hyper-parameters
with the entire train-set. The train-set AUROC was 0.93 and the test-set
AUROC was 0.84. The AUPR of the train-set was 0.66 and the test-set AUPR
was 0.39 (Figure 2A).

@@

The top 30 important predictors are shown (Figure 3). The coefficient is
the parameter of the predictor which represents the effect of the
predictor on prediction . IGF1R mRNA expression was the strongest
negative predictor, and PTEN was the strongest positive predictor. Both
IGFR1R and PTEN are key players in the tyrosine kinase pathway . The
cancer types were important predictors. Some cancer types including
uterine carcinosarcoma (UCS), bladder urothelial carcinoma (BLCA),
pancreatic adenocarcinoma (PAAD), lymphoid neoplasm diffuse large B-cell
lymphoma (DLBC) were the strongest predictors.

@@

Our model showed good performance in predicting PIK3CA mutations in
various cancer types. Our data suggested that the supervised elastic net
penalized logistic regression model could be applied not only to the RAS
activation pathway, but also to other genomic alterations. Both the RAS
activation pathway and PIK3CA mutations are key, common cancer genomic
alterations. When mutated, they exert significant effect on gene
expression in cells. However, the supervised elastic net penalized
logistic regression model cannot be generalized or applied to other
genomic alterations. It might be a challenging prediction of genomic
alterations that are infrequent or have a weak effect on gene
expression.

Prediction modeling from the TCGA pan-cancer dataset can be limiting in
terms of data preprocessing. The gene expression data is processed by
between-sample normalization to remove batch effects. If the model has
been trained from between-sample normalization, a new sample cannot be
exactly preprocessed with normalization which was done on trainset. A
model based on gene expression from the TCGA pan-cancer dataset is
limited in terms of data preprocessing. It is necessary to develop a
preprocessing method that is independent of a dataset, to apply gene
expression data to the prediction model.

Our PIK3CA prediction model was similar to the RAS activation prediction
model in terms of AUROC (0.84). However the AUPR of our model was lower
than the RAS activation model (0.39 versus 0.63). The reason for our
lower AUPR may be explained by the low prevalence rate of PIK3CA
mutations, and an imbalanced dataset. The model for RAS activation
trained with cancer types with more than 0.05 prevalence of RAS
activation to avoid imbalance classification problem. We included all
cancer types in our modeling process. The lower prevalence rate of
target variables meant our dataset had a lower AUPR baseline. In the
sub-analysis performance of each cancer type, the cancer types with
higher PIK3CA mutation rates showed better AUPRs.

Our model included cancer types as predictors, and they were stronger
predictors than gene expression. The varying prevalence of PIC3CA
mutations across cancer types may be a reason for the strong predictive
power of cancer types. If the cancer type was wrong or could not be
determined, our model performance was poor.

Some significant gene expression predictors were closely related to PTEN
and the PI3K pathway. PTEN and IGFR1R were the strongest gene expression
predictors, which has negative and positive predictive powers. IGF1R is
a tyrosine kinase receptor that activates PI3K {[}13{]}. {]}, and PTEN
is an important regulator of PIP\textsubscript{3} by dephosphorylating
PIP\textsubscript{3}, in contrast to PI3K {[}7{]}.

Several studies have attempted to predict genomic alterations from gene
expression data {[}4,14{]}. A study investigated PIK3CA mutation
predictions using gene-expression signatures which is a sum of the
average of the logarithmic gene expression . The model showed good
performance AUROC 0.71 in an independent test set {[}4,14{]}.Another
study predicted copy number alterations with gene expression, using a
multinomial logistic regression model with least absolute shrinkage and
selection operator (LASSO) parameters {[}15{]}. The prediction of the
1p/19q codel was very good, with an AUROC of 0.997, and gene-level
predictions were good, with an AUROC of 0.75 {[}15{]}. A Hidden Markov
Model Approach for Prediction of Genomic Alterations from Gene
Expression Profiling {[}16{]}. A logistic regression model was used for
MYCN gene amplification in neuroblastoma {[}17{]}.

Our study suggested that the prediction of genomic alterations using
gene expression data was possible, with good performance. However,
improved performances are required for clinical tests, and the
standardization of generation processing of gene expression data is also
needed .

@@

\begin{itemize}
\item
  Figure 1. Prevalence rate of PIK3CA mutations across cancer types.
  Cancer type abbreviations are explained in the S1 Appendix.
\item
  Figure 2. Summary of modeling results. (A) Left: receiver operating
  characteristic (ROC) curve. Right: precision-recall (PR) curve of
  train-set and test-set. The horizontal green line is the PIK3CA
  mutation rate (0.11) (B) Correlation between train-set and test-set of
  the area under the receiver operating characteristic curve (AUROC),
  and the area under the precision-recall curve (AUPR) among cancer
  types. The gray band is the 95\% confidence interval. Abbreviations
  are explained in the S1 Appendix. (C) Correlations between the PIK3CA
  mutation rate of the AUROC, and the AUPR.
\item
  Figure 3. Coefficient model. (A) Top 30 high mRNA coefficients. (B)
  Cancer type coefficients. Cancer types abbreviations are explained in
  the S1 Appendix.
\end{itemize}
